\documentclass[10pt]{article}



\begin{document}





\title*{Team Members}

\begin{itemize}

\item Amritpal Singh - C0748914
\item Manmohitpreet Singh - C0755086
\item Mantej Singh - C0749948
\item Sukhmanpreet Singh- C0748045

\end{itemize}



\section{ R1: Statement of Work  }

\subsection{Goal:   To write SOW using this software applictaion}


\subsection{ACTOR: The Project Manager(User)}

\subsection{SCENARIO: }

\begin{itemize}

  \item Step 1: The User opens the application.

  \item Step 2:The client is incited to type in a definite depiction of their work necessities.

  \item Step 3: The client is has a BUTTON to spare and leave their work when done. When they leave, the SOW is continued to information stockpiling.

\end{itemize}


\section{ R2: the Work Breakdown Structure  }

\subsection{Goal:  to create their SOW}





\subsection{ACTORS:}

\begin{itemize}

  \item   The Project Manager(User)

  \item  The Data Storage(which gets updated)

 \item The facilitators who will report the undertaking



\end{itemize}

						



\subsection{SCENARIO: }



\begin{itemize}

  \item Step 1: The User Activates the Screen in the Software for the Create SOW work.

  \item Step 2: The user enters required authentication id and password to log in.

  \item Step 3: The user goes to the main menu and selects the Item for Creating Work Breakdown Structure.

\item  Step 4: The user makes the WBS with DETAILED data including the directions for the colleagues to change over the undertaking necessities into noteworthy exercises..

\item Step 5: The user keeps decomposing the tasks into SUBTASKS until they arrive a task that can be easily done within one day as the user have function to decompose the TASKS.

\item Step 6: the user saves the WBS and updates into DATABASE STORAGE and exits the application. 

\end{itemize}



\section{Use Case for R3: TO create the resource register  }



\subsection{Use Case Name/Goal: }

To enable the project manager to create a List of available project resources such as Team members with skills



\subsection{ACTORS:}

\begin{itemize}

  \item   The Project Manager(User)

  \item  The Data Storage(which gets updated)



\end{itemize}

						



\subsection{SCENARIO: }



\begin{itemize}

  \item Step 1: The User Activates the Screen in the Software for the Create SOW work.

  \item Step 2: The user goes to the main menu and selects the Menu Item for Create /Modify Resource Register.

\item  Step 3: The User changes RESOURCES including Team individuals' profiles and other data.

\item Step 4:  The User saves the Resouce register and exits the application.

\end{itemize}



\end{document}

